%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{sebastian}{warnholz}{research assistant} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Berlin, Germany
%  LocalWords:  sa bibtex
%  LocalWords:  afriggeri
%  LocalWords:  www
%  LocalWords:  LaTeXTemplates
+49 157 3829663
~
\href{mailto:wahani@gmail.com}{wahani@gmail.com}
\href{http://wahani.github.io/}{wahani.github.io}
\href{http://www.wiwiss.fu-berlin.de/fachbereich/vwl/Schmid/Team/Warnholz.html}{fu://swarnholz}
\section{languages}
german mother tongue
english fluency
\section{programming}
{\color{red} $\varheartsuit$} R
\LaTeX, SQL, C++
\section{stats}
EViews, Excel, R, 
SPSS, Stata
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2009-2012}
{Master {\normalfont of Science}}
{Humboldt Universit\"at Berlin}
{in Statistics \\ Thesis: An Application of Regression Techniques to Online Marketing Data \\ The thesis explored different modelling strategies to predict conversion rates of customer cohorts for an online retail company using online marketing data.}

%------------------------------------------------

\entry
{2005--2009}
{Bachelor {\normalfont of Science}}
{Leuphana Universit\"at L\"uneburg}
{in Quantitative Economics and Social Sciences}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\subsection{as graduate}

\begin{entrylist}

%------------------------------------------------

\entry
{2012--Now}
{Freie Universit\"at Berlin}
{Berlin, Germany}
{research assistant \\
Teaching and consultancy are my main responsibilities in this position. The Freie Universit\"at has a statistical consultancy where I supervise the theses for bachelor, master and Ph.D. students. Furthermore I am involved in several small (1-2 persons) projects for companies as well as research institutes, e.g. ad-hoc data analysis or methodological reports.}

%------------------------------------------------

\entry
{2012--Now}
{INWT Statistics GmbH}
{Berlin, Germany}
{\emph{data scientist} \\ 
INWT (in numbers we trust) is a B2B consultancy specialised in services related to statistics and business intelligence. Projects range from analysing survey data, automated reporting and predictive modelling in a variety of settings. My role in the team is that of a hacker to build the infrastructure between several databases and our main programming language, R. This enables fast iterations in the cycle of 'data science projects'.
}

%------------------------------------------------

\end{entrylist}

%\pagebreak

\subsection{as student}

\begin{entrylist}

\entry
{2011--2012}
{Freie Universit\"at Berlin}
{Berlin, Germany}
{\emph{student assistant} \\
Alongside my master in statistics I worked in the statistical consultancy of the Freie Universit\"at Berlin. In this position my main responsibility was consultancy for bachelor, master and doctoral students. During that time I was responsible for the support of over 70 students.}

%------------------------------------------------

\entry
{2009-2012}
{DIW Berlin}
{Berlin, Germany}
{\emph{student assistant} \\
Position as a student assistant at the German Institute for Economic Research.}

%------------------------------------------------

\entry
{2009}
{TNS Infratest}
{Munich, Germany}
{\emph{internship} \\
Four month internship at a research institute for social sciences.}

%------------------------------------------------

\entry
{2008}
{Leuphana Universit\"at L\"uneburg}
{L\"uneburg, Germany}
{\emph{student assistant} \\
Tutor for Statistics II at the Department of Economics.}

%------------------------------------------------

\end{entrylist}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

%\section{awards}
%
%\begin{entrylist}
%
%%------------------------------------------------
%
%\entry
%{2011}
%{Postgraduate Scholarship}
%{School of Business, The University of California}
%{Awarded to the top student in their final year of a Bachelors degree. Mastered the art of filing accurate TPS reports.}

%------------------------------------------------

%\end{entrylist}%

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{teaching}

\begin{entrylist}

%------------------------------------------------

\entry
{2013-2015}
{lecture}
{Department of Economics, FU Berlin}
{CompStat: programming course for the R language. Students from the Master of Economics and Master in Statistics.}

%------------------------------------------------

\entry
{2012-2015}
{workshop}
{fu:stat}
{Introduction to statistic: one day and three days introductory statistics courses. Open for students and academic staff.}

%------------------------------------------------

\entry
{2012-2015}
{workshop}
{fu:stat}
{Introduction to panel data analysis with Stat or R: Intermediate level course focussing on methodology and either applications in Stata or R. Mostly visited by Ph.D. and master students.}

%------------------------------------------------

\entry
{2013-2014}
{lecture}
{Department of Economics, FU Berlin}
{Statistics II: undergraduate introductory statistics course.}

%------------------------------------------------

\entry
{2012-2014}
{workshop}
{fu:stat}
{Time series analysis with EViews: Advanced course for the analysis of cointegrated time series data. Two-day course. Open for students and academic staff.}

%------------------------------------------------

\entry
{2012}
{workshop}
{fu:stat}
{Do not trust any statistics!: a guide to quantitative research; one day course. Open for students and academic staff.}

%%------------------------------------------------
%
\end{entrylist}


%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{publications}

\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography

\printbibsection{unpublished}{accepted articles} % Print all research reports from the bibliography

\printbibsection{book}{books} % Print all books from the bibliography

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, title={conferences}, heading=bibheading]
\end{refsection}


\printbibsection{manual}{software}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} statistics, data analysis, blogging, web app creation, software design, learning new programming languages (Python, Scala, Haskell) \\ 
\textbf{personal:} billiards, cooking, reading, travelling


%----------------------------------------------------------------------------------------

\end{document}